Total Amount of Vaccinations Among Black population in the Target Zip Codes

### 2023-04-19 code/analysis_code/statisticalanalysis.qmd
Vax Rates

### creating a data frame that contains the variables that will be included in new linear regression mode. Just copying and pasting all of the totals generated from the `exploratoryanalysis.qmd` file
```{r}
#combined all relevant variables into 5 different data sets for each zip code. Got the black population totals for each zip code from  https://www.unitedstateszipcodes.org/31701/

Sum_by_month_31701 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                          Total = c(7797, 7780, 7755, 7773, 7792, 7817),
                          Intervention = c(1, 1, 1, 1, 1, 1),
                          Male_Total = c(3371, 3358, 3368, 3379, 3387, 3397),
                          Female_Total = c(4426, 4422, 4387, 4394, 4405, 4420),
                          Age_05_09 = c(123, 126, 126, 127, 127, 128),
                          Age_10_17 = c(642, 635, 633, 637, 630, 629),
                          Age_18_44 = c(3310, 3316, 3313, 3323, 3325, 3331),
                          Age_45_64 = c(3229, 3244, 3239, 3259, 3264, 3258),
                          Age_65Plus = c(2576, 2570, 2569, 2574, 2568, 2572),
                          Pop = c(16475, 16475, 16475, 16475, 16475, 16475))

Sum_by_month_31705 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                                Total = c(10383, 10327, 10303, 10301, 10337, 10348),                                 Intervention = c(1, 1, 1, 1, 1, 1),
                          Male_Total = c(4394, 4397, 4399, 4391, 4403, 4399),
                          Female_Total = c(5989, 5930, 5904, 5910, 5934, 5949),
                          Age_05_09 = c(210, 211, 209, 201, 202, 202),
                          Age_10_17 = c(1159, 1171, 1169, 1163, 1168, 1167),
                          Age_18_44 = c(5201, 5215, 5239, 5263, 5278, 5281),
                          Age_45_64 = c(4380, 4381, 4366, 4364, 4367, 4367),
                          Age_65Plus = c(2983, 3000, 2997, 2997, 2994, 2989),
                          Pop = c(24779, 24779, 24779, 24779, 24779, 24779))

Sum_by_month_31707 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                                Total = c(9035, 8985, 8997, 9005, 9035, 9042),                                 Intervention = c(1, 1, 1, 1, 1, 1),
                          Male_Total = c(3698, 3674, 3678, 3680, 3684, 3681),
                          Female_Total = c(5337, 5311, 5319, 5325, 5351, 5361),
                          Age_05_09 = c(275, 277, 280, 282, 284, 283),
                          Age_10_17 = c(1109, 1120, 1125, 1134, 1136, 1142),
                          Age_18_44 = c(5903, 5931, 5943, 5947, 5960, 5958),  
                          Age_45_64 = c(5130, 5120, 5125, 5123, 5133, 5140),
                          Age_65Plus = c(4200, 4204, 4195, 4206, 4202, 4189),
                          Pop = c(13884, 13884, 13884, 13884, 13884, 13884))

Sum_by_month_30815 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                          Total = c(8758, 8688, 8639, 8593, 8623, 8666),                                      Intervention = c(0, 0, 0, 0, 0, 0),
                          Male_Total = c(3526, 3514, 3503, 3484, 3489, 3498),
                          Female_Total = c(5232, 5174, 5136, 5109, 5134, 5168),
                          Age_05_09 = c(201, 213, 211, 215, 211, 211),
                          Age_10_17 = c(1116, 1113, 1115, 1118, 1115, 1114),
                          Age_18_44 = c(5001, 5009, 5020, 5026, 5025, 5032),
                          Age_45_64 = c(5026, 5017, 5020, 5009, 5013, 5020),
                          Age_65Plus = c(2816, 2825, 2827, 2814, 2828, 2832),
                          Pop = c(23481, 23481, 23481, 23481, 23481, 23481))

#um_by_month_30907 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                          #Total = c(4956, 4917, 4888, 4851, 4866, 4894),                                      Zip = c(30907, 30907, 30907, 30907, 30907, 30907),
                          #Male_Total = c(1947, 1943, 1926, 1900, 1913, 1919),
                          #Female_Total = c(3009, 2974, 2962, 2951, 2953, 2975),
                          #Age_05_09 = c(244, 239, 241, 236, 240, 242),
                          #Age_10_17 = c(1344, 1358, 1357, 1341, 1343, 1335),
                          #Age_18_44 = c(9203, 9217, 9238, 9245, 9253, 9246),
                          #Age_45_64 = c(6740, 6700, 6667, 6626, 6617, 6624),
                          #Age_65Plus = c(6632, 6633, 6639, 6635, 6633, 6623),
                          #Pop = c(7744, 7744, 7744, 7744, 7744, 7744)) 
#the 30907 zip code population of residents that are black does not match the vaccination data. also this zip code does not have a majority of residents that are black like other other 4 zip codes so I am going to leave it out of the statistical analysis

#combining all of the zip codes into one data set except for the 30907 data 
combined = rbind(Sum_by_month_31701, Sum_by_month_31705, Sum_by_month_31707, Sum_by_month_30815)
```

### creating a vaccination rate variable as the outcome 
```{r}
combined$Vax_rate = (combined$Total / combined$Pop) * 100
```

### Creating a linear regression model 
```{r}
lm_model2 <- lm(Vax_rate ~ Intervention + Male_Total + Female_Total + Age_05_09 + Age_10_17 + Age_18_44 + Age_45_64 + Age_65Plus, data = combined)

summary(lm_model2)
```
The results indicate that Intervention is a significant predictor of Vax_rate, as indicated by its estimate of 16.23 and its marginally significant p-value of 0.067. This means that there is some evidence that the intervention has an effect on the vaccination rate

Male_Total is a significant negative predictor of Vax_rate, with a coefficient of -0.0133 and a significant p-value of 0.0054. This suggests that a higher male population is associated with a lower vaccination rate

Among the age groups, Age_65Plus is a significant positive predictor of Vax_rate, with a coefficient of 0.0114 and a marginally significant p-value of 0.055. This means that a higher proportion of the population in the age group 65 and above is associated with a higher vaccination rate

Overall, the model has a high adjusted R-squared value of 0.9995, indicating that the predictor variables account for a large proportion of the variation in Vax_rate. However, it is important to note that with such a high R-squared value, overfitting may be a concern, and it may be necessary to perform additional checks, such as cross-validation or regularization

>>>>

```{r}

Sum_by_month_31701 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                          TOTAL_VAX_RATE = c(7797/12768, 7780/12768, 7755/12897, 7773/12897, 7792/12897, 7817/12897),
                          Intervention = c(1, 1, 1, 1, 1, 1),
                          Male_VAX_RATE = c(3371/5981, 3358/5981, 3368/5981, 3379/5981, 3387/5981, 3397/5981),
                          Female_VAX_RATE = c(4426/6787, 4422/6787, 4387/6916, 4394/6916, 4405/6916, 4420/6916),
                          Age_05_09_VAX_RATE = c(123/1058, 126/1058, 126/1058, 127/1058, 127/1058, 128/1058),
                          Age_10_17_VAX_RATE = c(642/1560, 635/1560, 633/1560, 637/1560, 630/1560, 629/1560),
                          Age_18_44_VAX_RATE = c(3310/5054, 3316/5054, 3313/5054, 3323/5054, 3325/5054, 3331/5054),
                          Age_45_64_VAX_RATE = c(3229/4628, 3244/4628, 3239/4628, 3259/4628, 3264/4628, 3258/4628),
                          Age_65Plus_VAX_RATE = c(2576/2886, 2570/2886, 2569/2886, 2574/2886, 2568/2886, 2572/2886),
                          TOTAL_RATE_DIFF = c(0, 7780/12768 - 7797/12768, 7755/12897 - 7780/12768, 7773/12897 - 7755/12897, 7792/12897 - 7773/12897, 7817/12897 - 7792/12897))

Sum_by_month_31705 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                                TOTAL_VAX_RATE = c(10383/21603, 10327/21572, 10303/21722, 10301/21887, 10337/21887, 10348/21887),                                 Intervention = c(1, 1, 1, 1, 1, 1),
                          Male_VAX_RATE = c(4394/9885, 4397/9854, 4399/10004, 4391/10004, 4403/10004, 4399/10004),
                          Female_VAX_RATE = c(5989/11718, 5930/11718, 5904/11718, 5910/11883, 5934/11883, 5949/11883),
                          Age_05_09_VAX_RATE = c(210/1639, 211/1639, 209/1639, 201/1639, 202/1639, 202/1639),
                          Age_10_17_VAX_RATE = c(1159/3311, 1171/3311, 1169/3311, 1163/3311, 1168/3311, 1167/3311),
                          Age_18_44_VAX_RATE = c(5201/11978, 5215/11978, 5239/11978, 5263/11978, 5278/11978, 5281/11978),
                          Age_45_64_VAX_RATE = c(4380/6468, 4381/6468, 4366/6468, 4364/6468, 4367/6468, 4367/6468),
                          Age_65Plus_VAX_RATE = c(2983/3497, 3000/3497, 2997/3497, 2997/3497, 2994/3497, 2989/3497), 
                          TOTAL_RATE_DIFF = c(0, 10327/21572 - 10383/21603, 10303/21722 - 10327/21572, 10301/21887 - 10303/21722, 10337/21887 - 10301/21887, 10348/21887 - 10337/21887))

Sum_by_month_31707 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                          TOTAL_VAX_RATE = c(9035/18045, 8985/18045, 8997/18045, 9005/18081, 9035/18081, 9042/18165),                                                       Intervention = c(1, 1, 1, 1, 1, 1),
                          Male_VAX_RATE = c(3698/8232, 3674/8232, 3678/8232, 3680/8232, 3684/8232, 3681/8232),
                          Female_VAX_RATE = c(5337/9813, 5311/9813, 5319/9813, 5325/9849, 5351/9849, 5361/9933),
                          Age_05_09_VAX_RATE = c(275/1583, 277/1702, 280/1702, 282/1702, 284/1702, 283/1702),
                          Age_10_17_VAX_RATE = c(1109/3001, 1120/3001, 1125/3001, 1134/3001, 1136/3001, 1142/3001),
                          Age_18_44_VAX_RATE = c(5903/11434, 5931/11434, 5943/11434, 5947/11434, 5960/11434, 5958/11434),
                          Age_45_64_VAX_RATE = c(5130/6051, 5120/6051, 5125/6051, 5123/6051, 5133/6051, 5140/6051),
                          Age_65Plus_VAX_RATE = c(4200/4259, 4204/4259, 4195/4259, 4206/4259, 4202/4259, 4189/4259), 
                          TOTAL_RATE_DIFF = c(0, 8985/18045 - 9035/18045, 8997/18045 - 8985/18045, 9005/18081 - 8997/18045, 9035/18081- 9005/18081, 9042/18165 - 9035/18081))

Sum_by_month_30815 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                          TOTAL_VAX_RATE = c(8758/19606, 8688/19736, 8639/19736, 8593/19736, 8623/19736, 8666/19736),                                                       Intervention = c(0, 0, 0, 0, 0, 0),
                          Male_VAX_RATE = c(3526/9066, 3514/9196, 3503/9196, 3484/9196, 3489/9196, 3498/9196),
                          Female_VAX_RATE = c(5232/10540, 5174/10540, 5136/10540, 5109/10540, 5134/10540, 5168/10540),
                          Age_05_09_VAX_RATE = c(201/2388, 213/2388, 211/2480, 215/2480, 211/2480, 211/2480),
                          Age_10_17_VAX_RATE = c(1116/3604, 1113/3604, 1115/3604, 1118/3604, 1115/3604, 1114/3604),
                          Age_18_44_VAX_RATE = c(5001/13358, 5009/13358, 5020/13358, 5026/13358, 5025/13358, 5032/13358),
                          Age_45_64_VAX_RATE = c(5026/8431, 5017/8431, 5020/8431, 5009/8431, 5013/8431, 5020/8431),
                          Age_65Plus_VAX_RATE = c(2816/3590, 2825/3590, 2827/3590, 2814/3590, 2828/3590, 2832/3590),
                          TOTAL_RATE_DIFF = c(0, 8688/19736 - 8758/19606, 8639/19736 - 8688/19736, 8593/19736 - 8639/19736, 8623/19736- 8593/19736, 8666/19736 - 8623/19736))

Sum_by_month_30907 = data.frame(Date = c("Sep","Oct","Nov","Dec","Jan","Feb"),
                          TOTAL_VAX_RATE = c(4956/9122, 4917/9189, 4888/9189, 4851/9189, 4866/9189, 4894/9189),                                                                      Intervention = c(0, 0, 0, 0, 0, 0),
                          Male_VAX_RATE = c(1947/4289, 1943/4289, 1926/4289, 1900/4289, 1913/4289, 1919/4289),
                          Female_VAX_RATE = c(3009/4833, 2974/4900, 2962/4900, 2951/4900, 2953/4900, 2975/4900),
                          Age_05_09_VAX_RATE = c(244/2174, 239/2174, 241/2174, 236/2174, 240/2174, 242/2174),
                          Age_10_17_VAX_RATE = c(1344/4070, 1358/4070, 1357/4070, 1341/4070, 1343/4070, 1335/4070),
                          Age_18_44_VAX_RATE = c(9203/14571, 9217/14571, 9238/14571, 9245/14571, 9253/14571, 9246/14571),
                          Age_45_64_VAX_RATE = c(6740/10362, 6700/10362, 6667/10362, 6626/10362, 6617/10362, 6624/10362),
                          Age_65Plus_VAX_RATE = c(6632/6995, 6633/6995, 6639/6995, 6635/6995, 6633/6995, 6623/6995), 
                          TOTAL_RATE_DIFF = c(0, 4917/9189 - 4956/9122, 4888/9189 - 4917/9189, 4851/9189 - 4888/9189, 4866/9189 - 4851/9189, 4894/9189 - 4866/9189))

#combining all of the zip codes into one data set except for the 30907 data 
combined = rbind(Sum_by_month_31701, Sum_by_month_31705, Sum_by_month_31707, Sum_by_month_30815,Sum_by_month_30907)
```

### Creating a linear regression model 
```{r}
lm_model2 <- lm(TOTAL_RATE_DIFF ~ TOTAL_VAX_RATE + Intervention + Male_VAX_RATE + Female_VAX_RATE + Age_05_09_VAX_RATE + Age_10_17_VAX_RATE + Age_18_44_VAX_RATE + Age_45_64_VAX_RATE + Age_65Plus_VAX_RATE, data = combined)

summary(lm_model2)
```
